Novel Methods for Characterizing Peaks from Direct Injection FT-MS Experiments

### 2019-11-14 peakcharacterization_manuscript.Rmd
using the right object
generating comparisons of normalization factors across three different normalization methods

@@

```{r rsd_table, results = 'asis'}
drake::loadd(rsd_table_rsd_data)
knitr::kable(rsd_out, digits = 3)
```

>>>>

```{r normalization_factors}
loadd(normalization_plot_normalization_values_data_4)
normalization_plot_normalization_values_data_4
```

@@

```{r rsd_table, results = 'asis'}
drake::loadd(rsd_table_rsd_data)
knitr::kable(rsd_table_rsd_data, digits = 3)
```
